---
title: 使用paletteer
draft: true
categories: [dataviz]
date: "2024-05-16"
date-modified: "`r Sys.Date()`"
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(paletteer)
theme_set(hrbrthemes::theme_ipsum_rc())
```

The palettes are divided into 2 groups; discrete and continuous. For discrete palette you have the choice between the fixed width palettes and dynamic palettes.

This package includes 2759 palettes from 75 different packages and information about these can be found in the following data.frames: `palettes_c_names`, `palettes_d_names` and `palettes_dynamic_names`. Additionally this [github repo](https://github.com/EmilHvitfeldt/r-color-palettes) showcases all the palettes included in the package and more.

```{r}
palettes_c_names
```

```{r}
palettes_d_names
```

## Examples

All the palettes can be accessed from the 3 functions `paletteer_c()`, `paletteer_d()` and `paletteer_dynamic()` using the by using the syntax packagename::palettename.

```{r}
paletteer_d(`"awtools::a_palette"`)
```

```{r}
paletteer_dynamic(`"cartography::blue.pal"`, n = 4)
```

## ggplot2 scales

```{r}
iris %>% 
  ggplot(aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point(size = 2.5) +
  scale_color_paletteer_d(`"ButterflyColors::astraptes_fulgerator"`)
```
